---
title: "HW4 Time Series"
author: "Curtis Zhuang"
date: "2021/4/26"
output: html_document
---


```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo = FALSE, warning = FALSE, include = FALSE}
library(forecast)
library(fpp)
library(TSA)
library("readr")
library('data.table')
library("rio")
```

<br>

#### **Question 1:**
#### Combine the data from the 16 files into a single dataset and plot it.
```{r}
### Convert xls to csv

# dat_path <- paste0(getwd(), '/Traffic Flow Data')
# xls <- dir(path = dat_path, pattern = "xls")
# created <- mapply(convert, xls, gsub("xls", "csv", xls))
# unlink(xls) # delete xlsx files


### read all csv and combine
filenames <- gsub("\\.csv$","", list.files(pattern="\\.csv$"))

for(i in c(1:16)){
  assign(paste0('dat', i), fread(paste(filenames[i], ".csv", sep=""),  select = c(3, 5), blank.lines.skip = TRUE))}

### Combine
dat = rbind(dat2[5:28], dat3[5:28], dat4[5:28], dat5[5:28], dat6[5:28], dat7[5:28], dat8[5:28], 
            dat9[5:28], dat10[5:28], dat11[5:28], dat12[5:28], dat13[5:28], dat14[5:28], 
            dat15[5:28], dat16[5:28], dat16[5:28], dat1[5:28])

### Rename
names(dat)[names(dat) == "...5"] <- "Traffic"
names(dat)[names(dat) == "...3"] <- "Time"


dat$Traffic <- as.numeric(dat$Traffic)


### plot
plot(ts(dat$Traffic))
```

<br>


#### **Question 2:**
#### Split the dataset into a training dataset which includes 6/16/2013 - 6/30/2013 samples and a test dataset which includes 7/1/2013 samples and plot the ACF and PACF.

```{r}
train <- dat[1: 384]

test <- dat[385:408]

### plot
#firstHour <- 24*(as.Date("2013-06-16 01:00:00")-as.Date("2013-01-01 00:00:00"))
#secondHour <- 24*(as.Date("2013-07-01 01:00:00")-as.Date("2013-01-01 00:00:00"))

#train_dt <- ts(train$Traffic, start = c(2013, 6, 16), frequency=24*365)
#test_dt <- ts(train$Traffic, start = c(2013, secondHour), frequency=24*365)

win.graph(width=6, height=6,pointsize=12)
tsdisplay(ts(dat$Traffic))
```

**We see that from PACF there is autocorrelation invovled with p = 2.**


<br>


#### **Question 3:**
#### Build an ğ´ğ‘…ğ¼ğ‘€ğ´(ğ‘,ğ‘‘,ğ‘) model using the training dataset and R auto.arima() function. Change the values of ğ‘ and ğ‘ and determine the best model using AICc and BIC values. Do AICc and BIC select the same model as the best model? For each derived model, review the residual plots for the residuals ACF and normality.

```{r}
### Auto-arima
train_dat <- ts(train$Traffic)
fit<-auto.arima(train_dat, trace = TRUE, lambda = 'auto')
print(fit)

# Find other p, q
res = data.frame(model=1, AICc=1, BIC=1)
ind = 1


## Based on PACF graph, we will keep p = 2 constant
for (q in seq(0,3)){
  for (d in seq(0,2)){
    m.trial = Arima(train_dat, order=c(2,d,q))
    res[ind, "model"] = paste0(2,d,q, collapse = ",")
    res[ind, "AICc"] = m.trial$aicc
    res[ind, "BIC"] = m.trial$bic
    ind = ind + 1
  }
}

res

two_three <- Arima(train_dat, order=c(2,0,3))
two_two <- Arima(train_dat, order=c(2,0,2))

checkresiduals(two_three)
checkresiduals(two_two)
```
**Check the residuals for (2,0,3) and (2,0,2), we see that in both cases Ljung-Box gives us a p value smaller than 0.05 which suggests both have a time series component. From the ACF plot, we see that both of them do not have white noise as residuals, thus there may be seasonality involved.**


<br>


#### **Question 4:**
#### Build a day of the week seasonal ğ´ğ‘…ğ¼ğ‘€ğ´(ğ‘,ğ‘‘,ğ‘)(ğ‘ƒ,ğ‘„,ğ·)ğ‘   model using the training dataset and R auto.arima() function.

```{r}
train_tssea <- ts(train$Traffic, frequency = 7*24)
season_fit<-auto.arima(train_tssea, trace = TRUE)

season_fit
```
**Resulting Arima model is (1,0,1)(0,1,0)[168] as frequency is 24 hours * 7 days**

<br>


#### **Question 5:**
#### Use the ğ´ğ‘…ğ¼ğ‘€ğ´(ğ‘,ğ‘‘,ğ‘)(ğ‘ƒ,ğ‘„,ğ·)ğ‘  model from Question 4 to forecast for July 1st (which is a Monday). Plot your result.

```{r}
prediction_wk <- forecast(season_fit, h = 24)
prediction_wk
plot(prediction_wk)
```



<br>


#### **Question 6:**
#### Build a hour of the day seasonal ğ´ğ‘…ğ¼ğ‘€ğ´(ğ‘, ğ‘‘, ğ‘)(ğ‘ƒ, ğ‘„, ğ·)ğ‘ model using the training dataset and R auto.arima() function.

```{r}
train_hr <- ts(train$Traffic, frequency = 24)
hr_fit <- auto.arima(train_hr, trace = TRUE, lambda = 'auto')
hr_fit
```
**Resulting Arima model is (1,0,0)(2,1,0)[24] as frequency is 24 hours * 1 day**

<br>


#### **Question 7:**
#### Use the ğ´ğ‘…ğ¼ğ‘€ğ´(ğ‘, ğ‘‘, ğ‘)(ğ‘ƒ, ğ‘„, ğ·)ğ‘  model from Question 6 to forecast for July 1st (which is a Monday). Plot your result.
```{r}
prediction_day <- forecast(hr_fit, h = 24)
prediction_day
plot(prediction_day)
```


<br>


#### **Question 8:**
#### Compare the forecast of the models from Questions 5 and 7 for July 1 8:00, 9:00, 17:00 and 18:00, which model is better (Questions 4 or 6)?
```{r}
Jul <- data.frame(Time = test$Time[c(8, 9, 17, 18)],
                  Week = prediction_wk$mean[c(8, 9, 17, 18)], 
                  Day = prediction_day$mean[c(8, 9, 17, 18)],
                  Actual = test$Traffic[c(8, 9, 17, 18)])

Jul
```
**Based on comparison I think the model from Q4 which is the model with week as frequency is better.**



















