---
title: "Time Series HW2"
author: "Curtis Zhuang"
date: "2021/4/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r import library, echo = FALSE, include = FALSE}
library(tseries)
library(forecast)
library(fpp)
library(lubridate)
library(ggplot2)
```

<br>

#### 1. Load the visitors.rda dataset, make a time plot of your data and describe the main features of the series.

```{r Q1}
load('visitors.rda')

y_quarterly <-  ts(visitors$Arrivals, start=c(1981, 1), frequency=4)

plot(y_quarterly, main = 'Visitors in Australia from US', xlab = 'Quater')
```

**Based on the graph, we see that the trend of visitors is positive overall and there is seasonality involved which happens yearly. The peak is during winter quarters. The level of the data also increases over time.**

<br>

#### 2. What is the appropriate Holt-Winters method for this data set (multiplicative / additive)? why?

```{r Q2}
# Additive
fit_add <- decompose(y_quarterly, type="additive")

plot(fit_add)

# Multiplicative
fit_mult <- decompose(y_quarterly, type="multiplicative")

plot(fit_mult)
```

**Based on the two plots, I think a multiplicative time series fits better. From graph of Q1, we see that for each rise and fall cycle, the distance between peak and bottom becomes larger and then fluctutates, and thus additive will not be ideal in this case.**

<br>

#### 3.Use the hw() function to forecast the next 16 quarters using Holt-Winters’ methods.

• Linear trend with additive seasonality
```{r, results = 'hide'}
fit_hw_add_1 <- hw(y_quarterly, h=16, seasonal="add",damped=FALSE)
summary(fit_hw_add_1)
```

• Linear trend with multiplicative seasonality
```{r, results = 'hide'}
fit_hw_mul_1 <- hw(y_quarterly, h=16, seasonal="mult",damped=FALSE)
summary(fit_hw_mul_1)
```

• Linear trend with additive seasonality and damping
```{r, results = 'hide'}
fit_hw_add_2 <- hw(y_quarterly, h=16, seasonal="add",damped=TRUE)
summary(fit_hw_add_2)
```

• Linear trend with multiplicative seasonality and damping
```{r, results = 'hide'}
fit_hw_mul_2 <- hw(y_quarterly, h=16, seasonal="mult",damped=TRUE)
summary(fit_hw_mul_2)
```

• Seasonal Naive
```{r, results = 'hide'}
fit_sn <- snaive(y_quarterly, h = 16)
summary(fit_sn)
```

<br>

#### 4.Use the accuracy() function to compare the Root-Mean-Square-Error (RMSE) values of the forecasts from the various methods. Which do you prefer and why?

```{r}
rmse_hw_add_no_damp <- accuracy(fit_hw_add_1)[2]
rmse_hw_mul_no_damp <- accuracy(fit_hw_mul_1)[2]
rmse_hw_add_damp <- accuracy(fit_hw_add_2)[2]
rmse_hw_mul_damp <- accuracy(fit_hw_mul_2)[2]
rmse_sn <- accuracy(fit_sn)[2]

paste(rmse_hw_add_no_damp, rmse_hw_mul_no_damp, rmse_hw_add_damp, rmse_hw_mul_damp, rmse_sn, sep = ", ")
```

**I prefer using Holt-Winters’ method with linear trend, multiplicative seasonality and with damping, as it provides me with the smallest RMSE = 7460.**

<br>

#### 5.Use the checkresiduals() function to check that the residuals from the best model look like white noise and provide a summary of the model’s smoothing parameters using the summary() function.

```{r}
checkresiduals(fit_hw_mul_2)

summary(fit_hw_mul_2)
```
**From our previous finding in Q2, I think the best model is multiplicative seasonality with damping. The smoothing parameters for the best model are: $\alpha = 0.52, \beta = 0.0027, \gamma = 1e-04, \phi = 0.98.$**

```{r}
checkresiduals(fit_hw_add_2)

summary(fit_hw_add_2)
```

**However, if we only look at the ACF alone considering white noise, the best model is the additive seasonality with damping, and the smoothing parameters for that are: $\alpha = 0.4702, \beta  = 1e-04, \gamma = 0.0761, \phi = 0.98$**











