---
title: "HW3_TS"
author: "Curtis Zhuang"
date: "2021/4/19"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo = FALSE, warning = FALSE, include = FALSE}
library(tseries)
library(forecast)
library(fpp)
library(TSA)
library(dplyr)
```

<br>

#### **Question 1:**
#### Load the usgdp.rda dataset and split it into a training dataset (1960 - 2012) and a test dataset (2013 - 2017)
```{r}
load('usgdp.rda')

train <- subset(usgdp, usgdp$Year < 2013)

test <- subset(usgdp, usgdp $ Year > 2012)

head(train)
```

<br>


#### **Question 2:**
#### Plot the training dataset. Is the Box-Cox transformation necessary for this data?

```{r}
# convert to time series
train_gdp <- ts(train$GDP, start= 1960, frequency = 1)
test_gdp <- ts(test$GDP, start= 2013, frequency = 1)

autoplot(train_gdp)

# find the best lambda for transformation
lambda <- BoxCox.lambda(train_gdp)
lambda

train_gdp %>% BoxCox(lambda = lambda) %>% autoplot()

# do transformation based on the best lambda 
trans_gdp <- BoxCox(train_gdp, lambda = lambda)
```
**We want to do a transformation with lambda = 0.23 because the original graph as we see is a little concave and we want to make it straight.**


<br>


#### **Question 3:**
#### Plot the 1st and 2nd order difference of the data. Apply KPSS Test for Stationarity to determine which difference order results in a stationary dataset.

```{r}
## 1st difference
plot(diff(trans_gdp))

## 2nd difference
plot(diff(diff(trans_gdp)))

## kpss for 1st and 2nd order
kpss.test(diff(trans_gdp), null = c("Level", "Trend"), lshort = TRUE)
kpss.test(diff(diff(trans_gdp), null = c("Level", "Trend"), lshort = TRUE))
```

**We can choose order 1 as p = 0.1 when using first order. And as the null hypothesis is stationary so we do not want to reject null hypothesis.**

<br>


#### **Question 4:**
#### Fit a suitable ARIMA model to the training dataset using the auto.arima() function. Remember to transform the data first if necessary. Report the resulting 𝑝,𝑑,𝑞 and the coefficients values.

```{r}
fit <- auto.arima(train_gdp, trace = TRUE, lambda = 'auto')
fit

Arima(train_gdp, order = c(1,1,0), lambda = lambda, include.drift = T)
```
**In this case AR order p = 1, transformation coefficient d = 1 and moving average q = 0.  AR coefficient is 0.4728 with a drift of 50.3366.**


<br>


#### **Question 5:**
#### Compute the sample Extended ACF (EACF) and use the Arima() function to try some other plausible models by experimenting with the orders chosen. Limit your models to 𝑞,𝑝 ≤2 and 𝑑≤2. Use the model summary() function to compare the Corrected Akaike information criterion (i.e., AICc) values (Note: Smaller values indicated better models).

```{r}
eacf(trans_gdp)

# p = 1, d = 1, q = 1
a111 <- Arima(train_gdp, order = c(1,1,1), lambda = lambda, include.drift = T)
summary(a111)

# p = 1, d = 1, q = 2
a112 <- Arima(train_gdp, order = c(1,1,2), lambda = lambda, include.drift = T)
summary(a112)

# p = 2, d = 1, q = 1
a211 <- Arima(train_gdp, order = c(2,1,1), lambda = lambda, include.drift = T)
summary(a211)

# p = 1, d = 2, q = 1
a121 <- Arima(train_gdp, order = c(1,2,1), lambda = lambda, seasonal = F)
summary(a121)

# p = 1, d = 2, q = 2
a122 <- Arima(train_gdp, order = c(1,2,2), lambda = lambda)
summary(a122)

# p = 2, d = 2, q = 1
a221 <- Arima(train_gdp, order = c(2,2,1), lambda = lambda)
summary(a221)

# p = 2, d = 2, q = 2
a222 <- Arima(train_gdp, order = c(2,2,2), lambda = lambda)
summary(a222)
```
**The best model from EACF is q = 1, d = 2, q = 1 and the AICc is 442.5 which is the smallest among all models.**


<br>


#### **Question 6:**
#### Use the model chosen in Question 4 to forecast and plot the GDP forecasts with 80 and 95 % confidence levels for 2013 - 2017 (Test Period).

```{r}
# get estimate from time series
test.fc <- forecast(fit, h = 5, level = c(80, 95))
test.fc

plot(forecast(fit,h=5),include=100)  
```

<br>


#### **Question 7:**
#### Compare your forecasts with the actual values using error = actual - estimate and plot the errors. (Note: Use the forecast $mean element for the forecast estimate)
```{r}
# plot the error
error_gdp <- test_gdp - test.fc$mean

error_gdp

plot(error_gdp)
```


<br>


#### **Question 8:**
#### Calculate the sum of squared errors
```{r}
SSE <- sum(error_gdp^2)
```
**SSE is $7.974*10^{23}$**



















